\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex
\usepackage{amssymb}


\title{SE 464 Project Demonstration -- Shots Fired}
\author{Sam Maier (scmaier), Addison Keizer (wcakeize), \\Dhruv Lal (d2lal), Shiranka Miskin (samiskin)}
%\date{}							% Activate to display a given date or no date
\let\endtitlepage\relax
\begin{document}
\maketitle


\clearpage

\section{Demo Summary}
\hspace*{5mm}
In this demo, we will demonstrate how our application works as whole. We will show
each part of the app and how we attempted to satisfy our two original user scenarios as
determined in Deliverable 1. The first user scenario was for a person to be able
to play with a group of friends. This would be done by allowing users to create
a private match in which they obtain a URL that their friends can use so that
everyone is entered in the same match. The second user scenario was a for a person
to be able to play a game without friends. Here they would enter a Quick Play mode
and be entered in a lobby with random people. The game would start once the maximum
number of players have entered the lobby, or at least the minimum number of players
have entered the lobby and a time limit has been reached.\\

With respect to the first user scenario, a user is presented with a splash screen.
They then click the "Private Match" button to start a new private game that they
can play with friends. The first person to create the private match will be presented
with a screen that shows a URL that they can provide to their friends. When someone
goes to this URL, they will be entered into the lobby. In this mode,
there needs to be 4 players in the lobby in order to start the game. Once there are 4
people in the lobby, the gameplay will commence.\\

With regards to the second user scenario, the user is presented with the same splash
screen. They then click the "Quick Play" button to join the lobby for a game with
random users who also wish to play this mode. Once there are at least 2 people in the
lobby, a 5 second countdown starts. Each time a person joins the lobby, the countdown
is restarted. Once the maximum number of players (4) have joined, or the countdown hits
0 when there are more than the minimum number of players (2), the game will start.\\

In both game modes, the gameplay is the same. Each person is given a character sprite
and is placed on one corner of the map. The character has unlimited ammo and ?? lives.
That being said, the character can be hit ?? number of times before they are eliminated
from the game. Once there is only 1 character remaining, the game is over and all users
are presented with a game over screen.\\

The user who won will see a slightly modified screen, congratulating them for being
the winner, whereas everyone else will see a game over screen. In both screens,
the user is presented with the option to begin a rematch or go to the main menu.
WILL UPDATE ONCE GAMEOVER FUNCTIONALITY CONFIRMED


\section{Status Report}
\hspace*{5mm}
Our app currently contains most of the functionality we specified in our original
proposal. Right now, a user has the option to play a game with friends through the
"Private Match" option and they have the option to play with random people using
the "Quick Play" option. This accounts for our requirement of a user being able to
join a matched game (through the "Quick Play" option) and for a user being able to play
with known people in an isolated environment (through the "Private Match" option).\\

Our app conforms to the 2D arena style game that we proposed where human players will
have their own character and must navigate through a 2D map. In terms of the player
movement itself, where each person is on their own computer, a user moves his character
using W to move up, S to move down, and A and D to move left and right respectively.
A user aims their gun using their mouse pointer and they fire bullets by left clicking
on the mouse. The player movement agrees with the movement requirements that we decided
in the proposal.\\

In terms of restrictions
to the user, we currently have each character set up such that they have ?? amount of
health and every player starts off with this amount of health. Each character also
has a weapon with infinite ammo, meaning that the user can just keep shooting without
having to worry about anything happening to the gun or bullets. Each of these restrictions
were specified in the style of game that we had in the proposal.\\

At the end of the game, the user is then presented with an option to play a rematch or
go back to the main menu.
CONFIRM ONCE GAME OVER FUNCTIONALITY DONE\\

CAN HANDLE MULTIPLE SIMULTANEOUS GAMES??\\

UNIMPLEMENTED FUNCTIONALITY??\\
TALK ABOUT NON-FUNCTIONAL PROPERTIES??\\


\end{document}
